A Systematic Literature Review on Extensions to Role Based Access Control

### 2013-04-25 paper/sections/core_rbac.tex
Spelling corrections.

RBAC provides effective and efficient permissions management for operations, especially when sharing resources withinin an organization.
Prior to the creation of the NIST RBAC standard, no general agreement on the definition 
of RBAC existed amongst practioners or within the research community. 
Without a unified definition of RBAC, software developers described similar concepts and features of RBAC models using different terminology. 
This lack of consistent terminology was shown to slow the implementation of RBAC \cite{o20102010}.  
Moreover, in cases where organizations were concerned with adopting RBAC,
evaluation and comparison of RBAC technologies developed by different vendors was difficult.
NIST, in collaboration with industry and academics, worked on defining a set of consensus RBAC concepts and terminology and proposed a standard for 
RBAC that addressed these cost and interoperability issues by developing a common definition that can be used across different vendors.

@@

The NIST RBAC standard model proposed by Ferraiolo et al. \cite{ferraiolo} and later adopted as the official standard for RBAC by the INCITS includes three levels of RBAC: core RBAC, hierarchal RBAC, and constrained RBAC.
Since the basis for our review is extensions to the RBAC standard model, we describe the core model, associated entities and other terminology encountered across the space of our review. Then, we describe hierarchal RBAC and constrained RBAC, which are developed by incoporating new features into the core RBAC.

@@

\subsection{Hierarchal RBAC}

Hierarchal RBAC model adds role hierarchies (RH) feature to core RBAC model.
This model incorporates a structure of roles in an organization using inheritance relationship among attributes such as roles.
The role structure in an organization may use
a role $r_1$, who inherits all permissions of another role $r_2$.
For example, a manager role may inherit all permissions of a employee role.
Role hierarchies help simplify access control policy creation and maintenance by reducing the number of
individual role assignments to a user. Formally, role inheritance relation is shown as \textit{RH} $\subseteq$ \textit{ROLES} $\times$ \textit{ROLES} describing many-to-many mapping role inheritance relation. 
General role hierarchies can be extended to use the concept of multiple inheritance where
a role $r_1$, who inherits all permissions from more than one roles.

>>>>

RBAC provides effective and efficient permissions management for operations, especially when sharing resources within an organization.
Prior to the creation of the NIST RBAC standard, no general agreement on the definition 
of RBAC existed among practitioners or within the research community. 
Without a unified definition of RBAC, software developers described similar concepts and features of RBAC models using different terminology. 
This lack of consistent terminology was shown to slow the implementation of RBAC \cite{o20102010}.  
Moreover, in cases where organizations were concerned with adopting RBAC,
evaluation and comparison of RBAC technologies developed by different vendors was difficult.
NIST, in collaboration with industry and academics, worked on defining a set of consensus RBAC concepts and terminology and proposed a standard for 
RBAC that addressed these cost and interoperability issues by developing a common definition that can be used across different vendors.

@@

The NIST RBAC standard model proposed by Ferraiolo et al. \cite{ferraiolo} and later adopted as the official standard for RBAC by the INCITS includes three levels of RBAC: core RBAC, hierarchical RBAC, and constrained RBAC.
Since the basis for our review is extensions to the RBAC standard model, we describe the core model, associated entities and other terminology encountered across the space of our review. Then, we describe hierarchical RBAC and constrained RBAC, which are developed by incorporating new features into the core RBAC.

@@

\subsection{Hierarchical RBAC}

Hierarchical RBAC model adds role hierarchies (RH) feature to core RBAC model.
This model incorporates a structure of roles in an organization using inheritance relationship among attributes such as roles.
The role structure in an organization may use
a role $r_1$, who inherits all permissions of another role $r_2$.
For example, a manager role may inherit all permissions of a employee role.
Role hierarchies help simplify access control policy creation and maintenance by reducing the number of
individual role assignments to a user. Formally, role inheritance relation is shown as \textit{RH} $\subseteq$ \textit{ROLES} $\times$ \textit{ROLES} describing many-to-many mapping role inheritance relation. 
General role hierarchies can be extended to use the concept of multiple inheritance where
a role $r_1$, who inherits all permissions from more than one roles.
